HO unification from object language to meta language

### 2024-03-28 paper/main.tex
wip

\begin{gather}
\lambda x y.F~y~x = \lambda x y.x\\
\lambda x. f~(F~x)~x = f~(\lambda y.y)
\end{gather}
Note that here $F$ is used with different arities, moreover
in the second problem the left hand side happens to be an
eta expansion (of $f (\lambda y.y)$) only after we discover that
$F = \lambda x\lambda y.y$ (i.e. that $F$ discards the $x$ argument).
Both problems are addressed in the next section.

@@

\begin{definition}[reduce-to]
  A term $t$ reduce to a name $x$, if $\exists \sigma, \sigma t = x$. In
  particular, for any term $t$, $\lambda x_1 \ldots x_n.t_{x_1\ldots x_n}$
  reduces to a bound variable $x$ if one of the three following cases is
  satisfied: 1) $n = 0$ and $t = x$; 2) $t$ is the application of $x$ to a list
  of terms $l$ and each $l_i$ reduces to $x_i$
  (since $\lambda x_1 \ldots x_n.x_{x_1\ldots x_n} = x$) ; 3) $t$ is a unification
  variable in \llambda with scope
  $s$, and for any $v \in \{ x, x_1 \ldots x_n \}$,
  there exists a $s_i \in s$, such that $s_i$ reduces to $v$
\end{definition}

>>>>

\begin{gather}
\lambda x y.F~y~x = \lambda x y.x\\
\lambda x. f~(F~x)~x = f~(\lambda y.y)
\end{gather}
Note that here $F$ is used with different arities, moreover
in the second problem the left hand side happens to be an
eta expansion (of $f (\lambda y.y)$) only after we discover (at run time)
that $F = \lambda x\lambda y.y$ (i.e. that $F$ discards the $x$ argument).
Both problems are addressed in the next section.

@@

\begin{definition}[reduce-to]
  A term $t$ reduce to a name $x$, if $\exists \sigma, \sigma t = x$. In
  particular, for any term $t$, $\lambda x_1 \ldots x_n.t_{x_1\ldots x_n}$
  reduces to a bound variable $x$ if one of the three following cases is
  satisfied: 1) $n = 0$ and $t = x$; 2) $t$ is the application of $x$ to a list
  of terms $l$ and each $l_i$ reduces to $x_i$
  (e.g. $\lambda x_1 \ldots x_n.x_{x_1\ldots x_n} = x$) ; 3) $t$ is a unification
  variable in \llambda with scope
  $s$, and for any $v \in \{ x, x_1 \ldots x_n \}$,
  there exists a $s_i \in s$, such that $s_i$ reduces to $v$
\end{definition}
